Methodology for Assessing the State of the Practice for Domain X

### 2020-03-16 StateOfPractice/Methodology/Methodology.tex
Updated website links

\hyperlink{https://github.com/pjmc-oliveira/HubListener}{GitHub repo}

@@

Cyclomatic:
\hyperlink{https://www.geeksforgeeks.org/cyclomatic-complexity/}{Intro}
\begin{itemize}
\item Cyclomatic Complexity
\end{itemize}

Halstead:
\hyperlink{https://www.geeksforgeeks.org/software-engineering-halsteads-software-metrics/}{Intro}
\begin{itemize}
\item Halstead Effort
\item Halstead Bugs
\item Halstead Length
\item Halstead Difficulty
\item Halstead Time
\item Halstead Vocabulary
\item Halstead Volume
\end{itemize}

@@

Test 1 on environment 3: 
\begin{itemize}
\item Repo: 3D Slicer \hyperlink{https://github.com/Slicer/Slicer}{Github repo}
\item Command line or web app: web app
\item Quick Analyze checked: Yes
\item Time Consumption: 96s
\item Errors/problems: data of total/open/closed issues are missing, data of
Cyclomatic and Halstead metrics are missing.
\end{itemize}

Test 2 on environment 3: 
\begin{itemize}
\item Repo: 3D Slicer \hyperlink{https://github.com/Slicer/Slicer}{Github repo}
\item Command line or web app: web app
\item Quick Analyze checked: No
\item Time Consumption: 4.3hrs
\item Errors/problems: the web app lost response after the analysis
\end{itemize}

Test 3/4 on environment 3: 
\begin{itemize}
\item Ao's repo \hyperlink{https://github.com/Ao99/e-commerce-django}{Github
repo}
\item Command line or web app: web app
\item Quick Analyze checked: Yes/No
\item Time Consumption: 121s/117s
\item Errors/problems: most data are missing
\end{itemize}

Test 5/6 on environment 3: 
\begin{itemize}
\item HubListener
\hyperlink{https://github.com/pjmc-oliveira/HubListener}{Github repo}
\item Command line or web app: web app
\item Quick Analyze checked: Yes/No
\item Time Consumption: 49s/131s
\item Errors/problems: none
\end{itemize}

>>>>

\href{https://github.com/pjmc-oliveira/HubListener}{GitHub repo}

@@

Cyclomatic:
\href{https://www.geeksforgeeks.org/cyclomatic-complexity/}{Intro}
\begin{itemize}
\item Cyclomatic Complexity
\end{itemize}

Halstead:
\href{https://www.geeksforgeeks.org/software-engineering-halsteads-software-metrics/}{Intro}
\begin{itemize}
\item Halstead Effort
\item Halstead Bugs
\item Halstead Length
\item Halstead Difficulty
\item Halstead Time
\item Halstead Vocabulary
\item Halstead Volume
\end{itemize}

@@

Test 1 on environment 3: 
\begin{itemize}
\item Repo: 3D Slicer \href{https://github.com/Slicer/Slicer}{Github repo}
\item Command line or web app: web app
\item Quick Analyze checked: Yes
\item Time Consumption: 96s
\item Errors/problems: data of total/open/closed issues are missing, data of
Cyclomatic and Halstead metrics are missing.
\end{itemize}

Test 2 on environment 3: 
\begin{itemize}
\item Repo: 3D Slicer \href{https://github.com/Slicer/Slicer}{Github repo}
\item Command line or web app: web app
\item Quick Analyze checked: No
\item Time Consumption: 4.3hrs
\item Errors/problems: the web app lost response after the analysis
\end{itemize}

Test 3/4 on environment 3: 
\begin{itemize}
\item Ao's repo \href{https://github.com/Ao99/e-commerce-django}{Github
repo}
\item Command line or web app: web app
\item Quick Analyze checked: Yes/No
\item Time Consumption: 121s/117s
\item Errors/problems: most data are missing
\end{itemize}

Test 5/6 on environment 3: 
\begin{itemize}
\item HubListener
\href{https://github.com/pjmc-oliveira/HubListener}{Github repo}
\item Command line or web app: web app
\item Quick Analyze checked: Yes/No
\item Time Consumption: 49s/131s
\item Errors/problems: none
\end{itemize}
